Improving Coconut Rhinoceros Beetle Breeding Site Detection Using Harmonic Radar

### 2021-09-30 FS-CRB-HR-report2.tex
added rept 2

@@

@@

% TODO: \usepackage{graphicx} required
\begin{figure}
	\centering
	\includegraphics[width=0.7\linewidth]{drone}
	\caption{RECCO harmonic radar device suspended from an agricultural drone.}
	\label{fig:drone}
\end{figure}

\listoftodos

@@

\textbf{Preliminary tests are promising. To date we have:
\begin{itemize}
	\item Used digital recordings of the RECCO's audio output to locate tags (Technical report)
	\item Flown the RECCO harmonic radar to a drone (Fig. \ref{fig:drone})
\end{itemize}
}

>>>>

\usepackage{graphicx}

@@

\textbf{Note to Reader:} Significant changes from the previous report are indicated by \textbf{bold-faced text}.

\bigskip

@@

\begin{figure}
	\centering
	\includegraphics[width=0.7\linewidth]{drone}
	\caption{RECCO harmonic radar device suspended from an agricultural drone piloted by Dr. Glenn Dulla, Guam Department of Agriculture.}
	\label{fig:drone}
\end{figure}

\clearpage

@@

\textbf{Preliminary tests are promising. To date we have:
\begin{itemize}
	\item Used digital recordings of the RECCO's audio output to locate tags (See Technical Report: Using a Cell Phone as a Datalogger for Handheld Harmonic Radar \url{https://github.com/aubreymoore/Harmonic-Radar/blob/master/experiments/techreport/techreport.pdf})	
	\item Flown the RECCO harmonic radar device attached to a drone (Fig. \ref{fig:drone})
\end{itemize}
}
